Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=9}
theme_set(theme_bw(25))
library(sorvi)
df = df0
dfs <- df %>% group_by(publication_year) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_year)) +
       geom_line() + geom_point() +
       xlab("Publication Year") + ylab("Paper per document")
p <- p + ggtitle("Average paper consumption per document")
print(p)
```

>>>>

```{r LIBER-11, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=5, fig.width=8, out.width="600px"}
theme_set(theme_bw(25))
library(sorvi)
dfs <- df0 %>% group_by(publication_decade) %>%
         summarize(paper.per.doc = mean(paper.consumption.km2, na.rm = T))
p <- ggplot(dfs, aes(y = paper.per.doc, x = publication_decade)) +
       geom_point() + geom_smooth(col = "black") +
       xlab("Publication year") + ylab("Paper per document") +
       ggtitle("Average paper consumption per document")
print(p)
```
